---
title: "Assignment2 - Real World Data Management Course SURV665"
author: "Elli Linek"
date: "18 6 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setup: Getting the data, organizing the prerequisites within R, creating the function (all from assignment1)
Download of relevant data sets: Source: https://ssl.isr.umich.edu/hrs/files2.php

Steps and relevant Information:
1) first of all the identification or the relevant data sets, in order to loas the relevant variables:
Sources: https://hrs.isr.umich.edu/documentation/questionnaires  and   https://hrs.isr.umich.edu/documentation/question-concordance


The final dataset should include the following information from waves 96, 98 and 00.
• household identifier:                          HHID (should be in all datasets?!) -> key?
• person number:                                 PN   (should be in all datasets?!) -> key?

-> dataset H96A_R (Section A is needed, (HRS 3) Core) -> dmgr
• a1b.birthdate year (only from ’96):            1996: E638  
• a2.born us? (only from ’96):                   1996: E639     
• a3.r education (only from ’96):                1996: E649
• a8.r race - masked (only from ’96):            1996: E667M
• a36.r religious pref (only from ’96):          1996: E732
• a37.english first language (only from ’96):    1996: E738

-> datasets H96B_R, H98B_R, H00B_R (Section B is relevant for most of these variables) -> health
• b1. rate health (from ’96, ’98 and ’00):       96/98/00: E769 F1097 G1226  
• b1a.rate health past (from ’96, ’98 and ’00):  96/98/00: E772 F1100 G1229
• b3.high blood pressure (from ’96, ’98 and ’00):96/98/00: E781 F1109 G1238
• b5.cancer (from ’96, ’98 and ’00):             96/98/00: E801 F1129 G1262
• cesd happy (from ’96, ’98 and ’00)(past weeks):96:       E988 
• cesd depressed (from ’96, ’98 and ’00):        96:       E985   

-> datasets H98C_R, H00C_R (Section C is relevant for these variables only for these years!) -> health_part2 for 98 and 00
• cesd happy (from ’96, ’98 and ’00)(past weeks):98/00:         F1496 G1672  
  (there exsist 2 variables cesd happy, again in section M:     F6304 G6551)
• cesd depressed (from ’96, ’98 and ’00):        98/00:         F1493 G1669  
  (there exsist 2 variables cesd depressed,again in section M:  F6301 G6548)
  
-> datasets H96F_H, H98F_H, H00F_H (section F is relevant for these varaibles) -> property&value
• f3.own-rent home (from ’96, ’98 and ’00):      96/98/00: E2226 F2743 G3061 
• f6.home value $ (from ’96, ’98 and ’00):       96/98/00: E2246 F2760 G3078  (i would expect lots of missings here)

• wave variable (you have to create for long data): needs to be created!

-> in total when i count all the different sections i have 9 data sources to load!
H96A_R (here i can use my function from assignment 1)
H96B_R, H98B_R, H00B_R
H98C_R, H00C_R
H96F_H, H98F_H, H00F_H

In addition and after searching the web for hints, i found a three variables that might work as a key for joining: 
1996 (HRS 3) Core	E	HHID	  HOUSEHOLD IDENTIFIER
1996 (HRS 3) Core	E	PN	    PERSON NUMBER
1996 (HRS 3) Core	E	ESUBHH	1996 SUB-HOUSEHOLD IDENTIFIER -> i might load that as well!
[ESUBHH, FSUBHH, GSUBHH - are the names for all three years!]


2) Alex' hint was to clean the data within long format and then to covert it to a wide data set, so i will work on that strategy
3) I will start to import the 96 data set, cause i can use my function from ass1
4) Based on that i will load and join the other 8 datasets, cleaning them later on  - after merging

#Setting up R:
```{r unzip}
library(tidyverse)
setwd("C:/Users/elli/IPSDS/SURV665_Introduction to Real World Data Management Section 1_summer 2019/assignments/ass")
list.files()
files <- list.files(pattern="*.zip")
dir.create('unzip')
seq_along(files)
dir <- "C:/Users/elli/IPSDS/SURV665_Introduction to Real World Data Management Section 1_summer 2019/assignments/ass/unzip"
for (i in seq_along(files)) {
  unzip(zipfile = files[i],
        exdir = dir)
}
```


```{r function ass11}
setwd("./unzip/")

#creating a function called “get_hrs_data()”:
get_hrs_data <- function(x) {
  content <- read_lines(str_c(x, ".DCT"))  #calling the relevant dct file
  content <- content[-1]                   #eliminating the rows as done before as well
  content <- content[-length(content)]
  #getting the meta data information
  meta_data <- read.table(textConnection(content),
                          header = F,
                          stringsAsFactors = F)
  colnames(meta_data) <- c("col", "type", "name", "size", "label")
  size <- as.numeric(str_extract(meta_data$size, "[0-9]+"))
  #calling the corresponding data file
  data <- read_fwf(str_c(x, ".DA"),
                   fwf_widths(size, meta_data$name))
  for (i in 1:ncol(data)) {
    attr(data[[i]], "lab") <- meta_data$label[i]
  }
  data
}

#setwd("./unzip/")
#test1 <- get_hrs_data("H00A_R")
```

#Assignment2:

```{r getting the data}
setwd("./unzip/")
#getting the first data set, including the "only 96" variables
dmgr96 <- get_hrs_data("H96A_R")
head(dmgr96)
#summary(dmgr96)

#hhid, pn, esubhh are included!
vrbls <- c("HHID", "PN", "ESUBHH" , "E638", "E639", "E649", "E667M", "E732", "E738")

#for better overview i should rename my selected variables (Exxx?)
dmgr96_sel <- dmgr96[vrbls]
head(dmgr96_sel)

#Renaming the last 6 variables
colnames(dmgr96_sel)[4:9] <- c("yearborn", "bornUSA", "education", "raceM", "religionPREF", "IstENGL")
head(dmgr96_sel)
summary(dmgr96_sel)

#seems the first data set is loaded, not yet cleaned but renamed for better understanding
#how to take care of NAs? I have to find out later, after joining, but i defenitely have to take care of!
```

```{r loading the other data sets}
#i will try to load all data sets within one step
setwd("./unzip/")
relevant_files <- c("H96B_R", "H98B_R", "H00B_R", "H98C_R", "H00C_R", "H96F_H", "H98F_H", "H00F_H")
#Loading sets for my topics: health1, health2 (for 98 and 00) and property&value
ALLdata <- map(str_c(relevant_files), get_hrs_data)

head(ALLdata[[1]]) #H96B_R
head(ALLdata[[2]]) #H98B_R
head(ALLdata[[3]]) #H00B_R

head(ALLdata[[4]]) #H98C_R
head(ALLdata[[5]]) #H00C_R

head(ALLdata[[6]]) #H96F_H
head(ALLdata[[7]]) #H98F_H
head(ALLdata[[8]]) #H00F_H

#i checked, all data sets are stored within the list, but i have to create a selection for each, taking the relevant varaibles into account

vrbls <- list(NULL)
vrbls[[1]] <- c("HHID", "PN", "ESUBHH", "E769", "E772", "E781", "E801", "E988", "E985")
ALLdata[[1]] <- ALLdata[[1]][vrbls[[1]]]
colnames(ALLdata[[1]])[4:9] <- c("health_96", "PASThealth_96", "HIGHblood_96", "cancer_96", "happy_96", "depr_96")
head(ALLdata[[1]])

vrbls <- list(NULL)
vrbls[[2]] <- c("HHID", "PN", "FSUBHH", "F1097", "F1104", "F1109", "F1129")
ALLdata[[2]] <- ALLdata[[2]][vrbls[[2]]]
colnames(ALLdata[[2]])[4:7] <- c("health_98", "PASThealth_98", "HIGHblood_98", "cancer_98")
head(ALLdata[[2]])

vrbls <- list(NULL)
vrbls[[3]] <- c("HHID", "PN", "GSUBHH", "G1226", "G1229", "G1238", "G1262")
ALLdata[[3]] <- ALLdata[[3]][vrbls[[3]]]
colnames(ALLdata[[3]])[4:7] <- c("health_00", "PASThealth_00", "HIGHblood_00", "cancer_00")
head(ALLdata[[3]])

vrbls <- list(NULL)
vrbls[[4]] <- c("HHID", "PN", "FSUBHH", "F1496", "F1493")
ALLdata[[4]] <- ALLdata[[4]][vrbls[[4]]]
colnames(ALLdata[[4]])[4:5] <- c("happy_98", "depr_98")
head(ALLdata[[4]])

vrbls <- list(NULL)
vrbls[[5]] <- c("HHID", "PN", "GSUBHH", "G1672", "G1669")
ALLdata[[5]] <- ALLdata[[5]][vrbls[[5]]]
colnames(ALLdata[[5]])[4:5] <- c("happy_00", "depr_00")
head(ALLdata[[5]])

vrbls <- list(NULL)
vrbls[[6]] <- c("HHID", "ESUBHH", "E2226", "E2246") #error: no PN here!
ALLdata[[6]] <- ALLdata[[6]][vrbls[[6]]]
colnames(ALLdata[[6]])[3:4] <- c("property_96", "propVALUE_96")
head(ALLdata[[6]])

vrbls <- list(NULL)
vrbls[[7]] <- c("HHID", "FSUBHH", "F2743", "F2760")
ALLdata[[7]] <- ALLdata[[7]][vrbls[[7]]]
colnames(ALLdata[[7]])[3:4] <- c("property_98", "propVALUE_98")
head(ALLdata[[7]])

vrbls <- list(NULL)
vrbls[[8]] <- c("HHID", "GSUBHH", "G3061", "G3078")
ALLdata[[8]] <- ALLdata[[8]][vrbls[[8]]]
colnames(ALLdata[[8]])[3:4] <- c("property_00", "propVALUE_00")
head(ALLdata[[8]])
```

```{r join}
setwd("./unzip/")

#Alex recommended to join yearwise first and later on the yearwise data sets into one, based on the "only 96 data"
#hrs96
hrs96 <- ALLdata[[1]] %>% 
inner_join(ALLdata[[6]], by = c("HHID", "ESUBHH"))%>% 
select(-ESUBHH)
head(hrs96)

#hrs98
hrs98 <- ALLdata[[2]] %>%
select(-FSUBHH) %>%
inner_join(ALLdata[[4]], by = c("HHID", "PN")) %>% inner_join(ALLdata[[7]], by = c("HHID", "FSUBHH"))%>% 
select(-FSUBHH)
head(hrs98)
#it took a while to find out, why i had FSUBHH.x and FSUBHH.y -  need to think of that for the other joins!!!

#hrs00
hrs00 <- ALLdata[[3]] %>%
select(-GSUBHH) %>%
inner_join(ALLdata[[5]], by = c("HHID", "PN")) %>% inner_join(ALLdata[[8]], by = c("HHID", "GSUBHH"))%>% 
select(-GSUBHH)
head(hrs00)

HRSjoined <- dmgr96_sel %>% #need to get rid of ESUBHH variable from demographic data set
select(-ESUBHH) %>%
inner_join(hrs96, by = c("HHID", "PN")) %>% inner_join(hrs98, by = c("HHID", "PN")) %>% inner_join(hrs00, by = c("HHID", "PN"))
head(HRSjoined)

#i used inner joins to assure that i have only units in my joined datasrt, that are in all three years, as the task asked for

HRSlong <- reshape(HRSjoined, idvar = 1:2, varying = 9:ncol(HRSjoined), sep = "_", timevar = "WAVE", direction = "long")
head(HRSlong)
#analogue to script/lecture, separation hint is important to get rid of the years in varaible names?!

uncleaned_HRSlong <- as.data.frame(HRSlong)
HRSwide <- reshape(data = uncleaned_HRSlong, idvar = c("HHID", "PN"), v.names = colnames(HRSlong)[9:length(HRSlong)],
timevar = "WAVE", sep = "_", direction = "wide")

rm(uncleaned_HRSlong)
HRSwide <- tbl_df(HRSwide)
save(HRSwide, HRSlong, file = "./E.Linek_ass2_uncleaned.RData")
#i can see the data file in my directory, so that part is saved

summary(HRSlong)
summary(HRSwide)
```


```{r cleaning the data}
setwd("./unzip/")
#now the cleaning part and the factorization of varaibles, as recommended i will do that within the long formated 

#function from Alex, in order to get reused during the cleaning actions 
#i changed the name in order to know what the function is about
hrs_yesORno <- function(x) {
  y <- case_when(x == 1 ~ "Yes",
                 x == 5 ~ "No")
  y <- as.factor(y)
  if (!is.null(attributes(x)$lab)) {
    attr(y, "lab") <- attr(x, "lab")
  }
  y
}


#start to clean the 1996 demografic data (first varaibles in my merged data set)
#whith the support of the pipe operator i call all the variables from the demographic data set at once
#after a first run and meeting tonight, i include the factors here too:
#again changing: after searching the web I include NA settings here

HRSlong <- HRSlong %>%
  mutate(yearborn = ifelse(yearborn > 9997, NA, yearborn),
         bornUSA = hrs_yesORno(bornUSA),
         education = ifelse(education > 20, NA, education),
         educationF = factor(education, labels = c("No formal education",
          "First grade",
          "Second grade",
          "Third grade",
          "Fourth grade",
          "Fifth grade",
          "Sixth grade",
          "Seventh grade",
          "Eighth grade",
          "Ninth grade",
          "Tenth grade",
          "Eleventh grade",
          "High school graduate",
          "Some college 1",
          "Some college 2",
          "Some college 3",
          "College graduate",
          "Post college")),
         raceM = ifelse(raceM > 7, NA, raceM),
         raceF = factor(raceM, labels = c("White/Caucasian", "Black/African American", "Other")),
         religionPREF = ifelse(religionPREF > 7, NA, religionPREF),
         religionF = factor(religionPREF, labels = c("Protestant", "Catholic", "Jewish", "No preference", "Other")),
         IstENGL = hrs_yesORno(IstENGL),
         health = ifelse(health > 5, NA, health),
         healthF = factor(health, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         PASThealth = ifelse(PASThealth > 3, NA, PASThealth),
         PASThealthF = factor(PASThealth, labels = c("Better", "About same", "Worse")),
         HIGHblood = hrs_yesORno(HIGHblood),
         cancer = hrs_yesORno(cancer),
         happy = hrs_yesORno(happy),
         depr = hrs_yesORno(depr),
         property = ifelse(property > 7, NA, property),
         propertyF = factor(property, labels = c("Own", "Rent", "Partial own", "Neither")),
         propVALUE = as.numeric(propVALUE),
         propVALUE = ifelse(propVALUE > 99999996, NA, propVALUE))

#Check for NAs
#check for lables
#check for created factors

Cleaned_HRSlong <- as.data.frame(HRSlong)
HRSwide <- reshape(data = Cleaned_HRSlong, idvar = c("HHID", "PN"), v.names = colnames(HRSlong)[9:length(HRSlong)],
timevar = "WAVE", sep = "_", direction = "wide")

rm(Cleaned_HRSlong)
HRSwide <- tbl_df(HRSwide)
save(HRSwide, HRSlong, file = "./E.Linek_ass2_cleaned.RData")
#i can see the data file in my directory, so that part is saved

head(HRSlong)
summary(HRSlong)
head(HRSwide)
summary(HRSwide)

#load("C:/Users/elli/IPSDS/SURV665_Introduction to Real World Data Management Section 1_summer 2019/assignments/ass/E.Linek_ass2_cleaned.RData")
```

```{r loop and\or function}
setwd("./unzip/")

#list of data sets, that are relevant (as i had used before)
relevant_files <- c("H96B_R", "H98B_R", "H00B_R", "H98C_R", "H00C_R", "H96F_H", "H98F_H", "H00F_H")
ALLdata <- map(str_c(relevant_files), get_hrs_data)

#all together taken the list of varaibles (i had that before too)
vrbls <- list(NULL)
vrbls[[1]] <- c("HHID", "PN", "ESUBHH", "E769", "E772", "E781", "E801", "E988", "E985") #E F G
vrbls[[2]] <- c("HHID", "PN", "FSUBHH", "F1097", "F1104", "F1109", "F1129")             #F G
vrbls[[3]] <- c("HHID", "PN", "GSUBHH", "G1226", "G1229", "G1238", "G1262")             #F G
vrbls[[4]] <- c("HHID", "PN", "FSUBHH", "F1496", "F1493")                               #F
vrbls[[5]] <- c("HHID", "PN", "GSUBHH", "G1672", "G1669")                               #G
vrbls[[6]] <- c("HHID", "ESUBHH", "E2226", "E2246")                                     #E
vrbls[[7]] <- c("HHID", "FSUBHH", "F2743", "F2760")                                     #F
vrbls[[8]] <- c("HHID", "GSUBHH", "G3061", "G3078")                                     #G 

columnCALLED <- list(NULL)
columnCALLED[[1]] <- c("HHID", "PN", "ESUBHH", "health_96", "PASThealth_96", "HIGHblood_96", "cancer_96", "happy_96", "depr_96")
columnCALLED[[2]] <- c("HHID", "PN", "FSUBHH", "health_98", "PASThealth_98", "HIGHblood_98", "cancer_98")
columnCALLED[[3]] <- c("HHID", "PN", "GSUBHH", "health_00", "PASThealth_00", "HIGHblood_00", "cancer_00")
columnCALLED[[4]] <- c("HHID", "PN", "FSUBHH", "happy_98", "depr_98")
columnCALLED[[5]] <- c("HHID", "PN", "GSUBHH", "happy_00", "depr_00")
columnCALLED[[6]] <- c("HHID", "ESUBHH", "property_96", "propVALUE_96")
columnCALLED[[7]] <- c("HHID", "FSUBHH", "property_98", "propVALUE_98")
columnCALLED[[8]] <- c("HHID", "GSUBHH", "property_00", "propVALUE_00")

#now to the loop?
#my problem is, that i dont know how to take care of the individual structures of my tasks (longer/shorter lists within different datasets, so i created a loop that is not that flexible, as it could probably be, but it loops through the renaming.

data.set <- list(NULL)
for (i in seq_along(ALLdata)) {
        data.set[[i]] <- ALLdata[[i]] %>%
        select(vrbls[[i]]) %>%
        setNames(columnCALLED[[i]])
}

#checking the results:
head(data.set[[1]])
head(data.set[[8]])


# #function (trial)
# rename_hrs_data <- function(data, selectionVRBLS, namesVRBLS) {
#             set <- ALLdata %>%
#                    select(vrbls) %>%
#                    setNames(columnCALLED)
#             set
# }
# 
# #follwing the recommendation at Github:
# #rename_hrs_data(ALLdata[[1]], selectionVRBLS = vrbls[[1]], namesVRBLS = columnCALLED[[1]])
# 
# #to dos as list, in order to call these later on:
# tasks <- list(data = ALLdata, selectionVRBLS = vrbls, namesVRBLS = columnCALLED)
# 
# #trying the pmap command to call the function and apply to all datasets within the list
# data.set2 <- pmap(tasks, rename_hrs_data)

#-> the so created data still needs to be cleaned, as done before/above in the original code...
```

