---
title: "Assignment1 - Real World Data Management Course SURV665"
author: "Elli Linek"
date: "8 6 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setup: Getting the data, organizing the prerequisites within R

##Download of relevant data sets:
Source: https://ssl.isr.umich.edu/hrs/files2.php
Download of 6 files: 3 da files, 3 sta files (ech file for the years 1996 1998 and 2000)
Saved under: "C:\Users\elli\IPSDS\SURV665_Introduction to Real World Data Management Section 1_summer 2019\assignments\ass1"

##Setting up R:
```{r prerequisites}
#tidyverse is already installed, so i will load the package and check for updates instead of installing 
library(tidyverse)
#update.packages(tidyverse_update())

#setting the according working directory:
setwd("C:/Users/elli/IPSDS/SURV665_Introduction to Real World Data Management Section 1_summer 2019/assignments/ass1")

#listing the files in my folder (all files, that are saved there)
list.files()
files <- list.files(pattern="*.zip")
files

#Result: I have 9 files within the folder, so 9 elements are listed, the data files are part of the list (still zip-files), as part of the command line below a list only including the zip-files is stored into the object "data_files"

#folder for unzipped data files created:
dir.create('unzip')

#loop, in order to unzip all 6 zip files and store them in the new directory:
seq_along(files)
dir <- "C:/Users/elli/IPSDS/SURV665_Introduction to Real World Data Management Section 1_summer 2019/assignments/ass1/unzip"
for (i in seq_along(files)) {
  unzip(zipfile = files[i],
        exdir = dir)
}

#removing the zip files from the assignment1 folder:
file.remove(files)

#6 files were deleted, the R console remarks 6 times "true" as a result
```

Short intermins resumee: the data files were downloaded, the files were unzipped into a new directory, the original folder was "cleaned", so all should be set up to start to work with the data.

```{r unzipped data files}
#now that the data files are unzipped, I am setting the working directory to the folder, where the data files are stored:

setwd("./unzip/")
list.files()
#258 files are stored within the folder "unzip"

#there are different types of files:
#Hyy*_R.DA  -> seems to be the raw data file, data entries per line per line/row per row
#Hyy*_R.DCT -> seems to contain additional meta data such as labels
#Hyy*_R.DO  -> seems to be a stata support file (not used for R)

#starting to look into the data: 
#From the assignment task: "For now we will import the “H00A_R” data." 
#I am follwoing the example from the tasks pdf file:
file_imp <- "H00A_R"
str_c(file_imp, ".DCT")
content <- read_lines(str_c(file_imp,".DCT"))
head(content)
summary(content)

# Eliminating two rows: the first and the last one, still following the example:
content <- content[-1]
#length(content)
content <- content[-length(content)]
head(content)
summary(content)

```

#Turning the data into a database, creating a loop and defining a function, including all steps of data-management done so far in "single steps"
```{r data}
setwd("./unzip/")

#loading the information out of content, storing it in the object meta_data, no header
meta_data <- read.table(textConnection(content),
                        header = FALSE,
                        stringsAsFactors = FALSE)

#checking back the object
str(meta_data)
colnames(meta_data) <- c("col", "type", "name", "size", "label")
head(meta_data)

#extracting the numbers, following the example:
meta_data$size
meta_data$size_nr <- as.numeric(str_extract(meta_data$size, "[0-9]+"))
meta_data$size_nr

#importing and saving data:
data <- read_fwf(str_c(file_imp, ".DA"),
                 fwf_widths(meta_data$size_nr,
                            meta_data$name))

#investigating the dataset, as it was asked for in the task:
str(data)
head(data)
summary(data)

#adding attributes to the variables:
attr(data[[1]], "lab") <- meta_data$label[1]

#checking the result for the Houshold ID-variable: 
attributes(data$HHID)
#The variable is labeled as "HOUSEHOLD IDENTIFIER"


#--> until here i was following stept by step the code examples from the assignment paper, now i am starting to create the loop, based on the earlier steps:

#Looping through the tasks, doing that for each column in “data” - so the tasks stay stable, but the column information need to be changed one by one - instead of [[1]] i will take [[i]] into account:
#each column is "ncol", taking all number of columns into account
ncol(data)
for (i in 1:ncol(data)) {
  attr(data[[i]], "lab") <- meta_data$label[i]
}

#trying to check other variables:
attributes(data$PN)
attributes(data$GPN_SP)
attributes(data$G1163)
attributes(data$G1176)
#Variables until the last column are labeled, even though without further description not all of them are interpretable 

#Finally, create a function called “get_hrs_data()”:
#First of all i am starting to set uo the function, naming it, and then getting all "relevant tasks" into its body":
get_hrs_data <- function(x) {
  content <- read_lines(str_c(x, ".DCT"))  #calling the relevant dct file
  content <- content[-1]                   #eliminating the rows as done before as well
  content <- content[-length(content)]
  #getting the meta data information
  meta_data <- read.table(textConnection(content),
                          header = F,
                          stringsAsFactors = F)
  colnames(meta_data) <- c("col", "type", "name", "size", "label")
  size <- as.numeric(str_extract(meta_data$size, "[0-9]+"))
  #calling the corresponding data file
  data <- read_fwf(str_c(x, ".DA"),
                   fwf_widths(size, meta_data$name))
  for (i in 1:ncol(data)) {
    attr(data[[i]], "lab") <- meta_data$label[i]
  }
  data
}

#as body of the function i set all the steps i did so far above, now just bringing it together, including the loop per columns, until all coulumns are done

#the function is now part of my environment, now i am trying to call it:
#taking the "HyyA_R" file for all three years, hoping i can compare these contentual wise.

setwd("./unzip/")
test1 <- get_hrs_data("H00A_R") #first file in the folder
head(test1)
summary(test1)

test2 <- get_hrs_data("H98A_R")
head(test2)

test3 <- get_hrs_data("H96A_R")
head(test3)

#Result: the function worked to create the test databases, getting the information out of the dct files as well the da files
#I was surprised by the different numbers of varibles, but that might be related to differences in the data files themselves (differences between the years)
#checking the console output i receive some "xxx parsing failures." could you maybe help me out with that? i could not find a way how to check what these message concretely refers to.

```


#Importing demographic data 
```{r demographics}
#for savety reason i set the unzip folder to be the defined working directory
setwd("./unzip/")

#Task1: creating dem as object, "calling" my function to load the data etc. into it:
dem <- get_hrs_data("H96A_R")

#checking the so created data base
head(dem)
summary(dem)
attributes(dem)

#Task2: using the sapply command to have a look at the attributes:
#?sapply
sapply(dem, attributes)
# A list of all variable names and its referring label is shown for all 75 variables

#Task3: Select the variables that have the following labels:
#• HOUSEHOLD IDENTIFIER        -> HHID
#• PERSON NUMBER               -> PN
#• A1B.BIRTHDATE YEAR          -> E638
#• A2.BORN US?                 -> E639
#• A3.R EDUCATION              -> E649
#• A8.R RACE - MASKED          -> E667M
#• A36.R RELIGIOUS PREF        -> E732
#• A37.ENGLISH FIRST LANGUAGE  -> E738

#I found all variables, and added the corresponding varaible name

#Task3: Selection of these variables, saving them into another object, so that i know its the selected ones:
variable_selection <- c("HHID", "PN", "E638", "E639", "E649", "E667M", "E732", "E738")
dem_selection <- dem[variable_selection]

#Task4: Renaming the last 6 variables, so i select columns 3 to 8 out of the saved selection object
colnames(dem_selection)[3:8] <- c("A1B", "A2", "A3.R", "A8.R","A36.R", "A37")
head(dem_selection)

#The table shows the new column names, so it has worked

```

#Import from multiple waves
```{r multiple waves}
#I set the unzip folder to be the defined working directory
setwd("./unzip/")

#Task1: Three data sets shall be imported now
#so first of all i will give the names of all three into an object, so that i can call this later on, and than i work with the created function:
years <- c("H96B_R", "H98B_R", "H00B_R")
data1 <- map(years, get_hrs_data) 
#I did not want to overwrite my object data from above so i changed the name into data1, i hope that is ok

#checking one of the data sets:
head(data1[[1]])

#Task2: Ussing again the sapply function to define relevant variable names.
sapply(data1[[1]], attributes)

#I have three elemnt in data1 in total, so i create a loop to do it for all three of them:
for (i in seq_along(data1)) {
  print(sapply(data1[[i]], attributes))
}

#Now looking for the asked variables:
#• HOUSEHOLD IDENTIFIER   -> HHID (i found this in all three data sets to be the same)
#• PERSON NUMBER          -> PN   (i found this in all three data sets to be the same)
#• B1.RATE HEALTH         -> E769, F1097, G1226
#• B1A.RATE HEALTH PAST   -> E772, F1104, G1229
#• B3.HIGH BLOOD PRESSURE -> E781, F1109, G1238
#• B5.CANCER              -> E801, F1229, G1262
#I have to admit it was not easy to find all the varaibles, i hope i selected the right ones!

#Further preparation for the "final" loop: 
#a) selecting the variables, I need to do that for all three elements in data1, i create an empty list, than storing all the varibales there
variable_selection <- list(NULL)
#now filling the object with all the information, for each year:
variable_selection[[1]] <- c("HHID", "PN", "E769", "E772", "E781", "E801")
variable_selection[[2]] <- c("HHID", "PN", "F1097", "F1104", "F1109", "F1129")
variable_selection[[3]] <- c("HHID", "PN", "G1226", "G1229", "G1238", "G1262")

#I need to prepare the wave variable too, for task b), i create the object wave to store the years there:
wave <- c("1996", "1998", "2000")
wave

#I tried, it did not work, so i create an empty list again to have another object where i can store the data:
data_object <- list(NULL)
data_object

#now finally after setting up the objects: looping the steps through, to fulfill the rename etc.:
for (i in seq_along(data1)) {
  data_object[[i]] <- data1[[i]][variable_selection[[i]]]
  colnames(data_object[[i]]) <- c("HHID", "PN", "B1", "B1.A", "B3", "B5")
  data_object[[i]]$wave <- wave[i]
}

data_object
#now there are 3 elements in it

#checking the content of the data_objects:
head(data_object[[1]])
summary(data_object[[1]])
head(data_object[[2]])
summary(data_object[[2]])
head(data_object[[3]])
summary(data_object[[3]])

#Task4: final step, turning it into one data base
#furhter information on the reduce command needed:
?reduce
?rbind
#now creating the object, combining the data_objects (lists?) there:
hrs_3waves <- reduce(data_object, rbind)
head(hrs_3waves)
summary(hrs_3waves)
dim(hrs_3waves)

#final step:
#i am going through the code, reformatting it for easier reading, checking or adding comments...

```





