---
title: "Web Scraping: Assignment 1"
author: "Elli Linek"
output: html_document
---


### 0. Preparation: Load packages

```{r load packages}
# enter your R code here

library(stringr)
library(tidyr)

```


### 1. The ultimate regular expression

Find a regular expression that matches any text!

```{r}
# enter your R code here

anytext <- "Which regular expression matches any text?"
str_subset(anytext, ".+")
answer <- ".+ matches any text"
answer
```

<span style="color:blue">
If you want to add a comment outside the R code block, use this <span> block! (just copy the <span>...</span> lines for future comments in the Rmd file.)
</span>


### 2. Finding strings that are matched by regular expressions

Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

a. [0-9]+\\$
b. b[a-z]{1,4}
c. .*?\\.txt$
d. \\d{2}/\\d{2}/\\d{4}
e. <(.+?)>.+?</\\1>

```{r}
# Example
str_extract_all("Phone 150$, TV 690$", "[0-9]+\\$") # Answer: this regex describes prices in dollars

#b
str_extract_all("birds, bees, bears, even bugs would match, monkeys would not", "b[a-z]{1,4}") # Answer: this regex extracts words starting with b followed by 1 to 4 other lower case letters (letters after b between 1 and 4)

#c
str_extract_all("list of files: textfile.txt, anothertextfile.txt, notatextfile.jpeg, neitheratextfile.ppt againatext.txt", ".*?\\.txt$") # Answer: extracts all text or characters that are before a string with .txt at the end, meaning .txt being the last phrase

#d
str_extract_all("it's a birthday on 19/03/1982","\\d{2}/\\d{2}/\\d{4}") # Answer: that regex is giving back structured dates: 2-digits per day, 2-digits per month and 4-digits for the year, all divided by /

#e
str_extract_all("<h1> here in between is a headline on first level within an html file </h1>","<(.+?)>.+?</\\1>") # Answer: the regex is refereing to a text between <...> and <...> where /1 is referenicating the first group again, just like it is within html logic


# enter your R code here to solve b. to e.
```


### 3. Manipulating an email address

Consider the mail address  datalover89[at]aol[dot]com. Now, complete the following tasks.

a. Transform the string to a standard mail format (i.e., replace the square brackets with the appropriate symbols) using regular expressions.
b. Now extract the local-part ("datalover89") and the domain ("aol") separately. 

```{r}
# enter your R code here

raw.data <- "datalover89[at]aol[dot]com"

#a
email<- str_replace_all(raw.data, pattern = "\\[at]" ,replacement = "@")
email<- str_replace_all(email, pattern = "\\[dot]" ,replacement = "\\.")
email

#b
str_match("datalover89@aol.com","(.*?)@(.*?)\\.")[-1]


```


### 4. A secret message
The following code hides a secret message. Crack it with R and regular expressions. Once you have cracked it, try to collapse the solution in one single string. <i>Hint: Some of the characters are more revealing than others!</i> 

secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"


```{r}

library(stringr)

 raw.data <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"
 
 secret <- unlist(str_extract_all(raw.data, "[[:upper:].!]"))
 secret <- paste( unlist(secret), collapse='')
 secret <- str_replace_all(secret, pattern = "\\." ,replacement = " ")
 secret
 
# enter your R code here
```


