---
title: 'Data confidentiality - Homework Assignment 2'
author: "Elisabeth Linek"
output:
  word_document: default
  html_document: default
---
#1 summaries as overview

```{r}
library('dplyr')

load("synthetic_cps.RData")

summary(cps)
summary(syn.data[[1]])
summary(syn.data[[2]])
summary(syn.data[[3]])
summary(syn.data[[4]])
summary(syn.data[[5]])

#1 checking for missings within data sets, just to check if i have to account for those

table(is.na(cps))
table(is.na(syn.data[[1]]))
table(is.na(syn.data[[2]]))
table(is.na(syn.data[[3]]))
table(is.na(syn.data[[4]]))
table(is.na(syn.data[[5]]))


```

#2 analysis, calculation of requested estimates for taxes

```{r}
##get point and variance estimate from each synthetic dataset as well as from cps (original data set)

m<-length(syn.data)
n<-nrow(cps)

q.i<-rep(NA,m)
u.i<-rep(NA,m)

for(i in 1:m){
	q.i[i]<-mean(syn.data[[i]]$tax)
	u.i[i]<-var(syn.data[[i]]$tax)/n
	} 

##more efficient way from lectures (trying out)
#q.i<-sapply(syn.data,function(x) mean(x$tax))
#u.i<-sapply(syn.data,function(x) var(x$tax)/nrow(x))

# necessary quantities to compute final variance
u.bar<-mean(u.i)
b.m<-var(q.i)


print(q.i)
print(u.i)
print(u.bar)
print(b.m)


#final estimates
q.bar<-mean(q.i)
T.p<-u.bar+b.m/m

print(q.bar)
print(T.p)

#cps data in comparison
mean(cps$tax)
var(cps$tax)/n


```


#3 analysis, calculation of requested estimates for race

```{r}
##get point and variance estimate from each synthetic dataset as well as from cps (original data set)

m<-length(syn.data)
n<-nrow(cps)

#Original data set cps

#Estimation of the proportion of blacks (race==2)
summary(cps$race)
cps$race.black <- ifelse(cps$race==2,1,0)
table(cps$race.black)

#Calculation of the proportion
race.m <- mean(cps$race.black) 
print(race.m)

#Variance of the point estimate
(race.m*(1-race.m))/n


#Synthetic data, analysising each dataset separately first (step a)
for (i in 1:5)
{syn.data[[i]]$black <- ifelse(syn.data[[i]]$race==2,1,0)}

#Proportions in the datasets
black.m <- rep(NA,5) 
for (i in 1:5)
{black.m[i]<- mean(syn.data[[i]]$black)}
print(black.m)

#Variance estimates
black.v <- rep(NA,5) #for variances
black.v <- (black.m*(1-black.m))/n
black.v

#Synthetic data, combining the results (step b)
#Proportion: final estimate
mean(black.m)

#Variance
#(b.m: Variability of point estimates)
var(black.m)

#(u.m: average variance estimation)
mean(black.v)

#combining the results
black.T.p <- mean(black.v) + var(black.m)/5
black.T.p

```

##compute the degrees of freedom
dfs<-(m-1)*(1+u.bar/(b.m/m))^2

##compute 95% confidence intervals
l.95.syn<-q.bar-qt(0.975,df=dfs)*sqrt(T.p)
u.95.syn<-q.bar+qt(0.975,df=dfs)*sqrt(T.p)

##compare results to original data
q.org<-mean(cps$income)
T.org<-var(cps$income)/nrow(cps)
l.95.org<-q.org-1.96*sqrt(T.org)
u.95.org<-q.org+1.96*sqrt(T.org)

syn.res<-cbind(l.95.syn,q.bar,u.95.syn)
org.res<-cbind(l.95.org,q.org,u.95.org)

res<-rbind(org.res,syn.res)
dimnames(res)<-list(c("org","syn"),c("lower95","mean.inc","upper95"))
print(res)


#4 complex analysis, regression model

```{r}

load("synthetic_cps.RData")

#first regression
reg1.cps<-lm(log(income)~tax+csp+age+as.numeric(educ)+marital+race+as.factor(sex)+ss,data=cps)
summary(reg1.cps)
print(reg1.cps)
#reg1.results<-cbind(summary(reg1.cps)$coef[,1],summary(reg1.cps)$coef[,2]^2)

#-----
#function as shown within example in lecture (stores all point and variance estimates)
func<-function(data){
 
###descriptive statistics
#inc.mean<-as.numeric(by(data$income,data$sex,mean))
#inc.var<-as.numeric(by(data$income,data$sex,var)/table(data$sex))
#inc.results<-cbind(inc.mean,inc.var)

#age.mean<-as.numeric(by(data$age,data$sex,mean))
#age.var<-as.numeric(by(data$age,data$sex,var)/table(data$sex))
#age.results<-cbind(age.mean,age.var)

###turn education variable into continuous variable
data$educ<-as.numeric(levels(data$educ))[data$educ]
#-----

#regressions (I tried several, until I `found` the fitting one)

#reg2.cps<-lm(log(income)~tax+csp+age+as.numeric(educ)+marital+race+sex+ss,data=cps)
#summary(reg2.cps)
#print(reg2.cps)
#reg2.results<-cbind(summary(reg2.cps)$coef[,1],summary(reg2.cps)$coef[,2]^2)

reg3.cps<-lm(log(income)~tax+csp+age+educ+marital+race+as.factor(sex)+ss,data=data)
summary(reg3.cps)
print(reg3.cps)
reg3.results<-cbind(summary(reg3.cps)$coef[,1],summary(reg3.cps)$coef[,2]^2)
 
dimnames(reg3.results)<-list(c("Intercept","tax","csp","age","educ","married, spouse absent","separated","divorced","Widowed","never married/single","unknown","Black","Am.Indian","Asian","SEX","SS"),c("estimate","variance"))
return(reg3.results)
  
}

#get estimates from synthetic data (a list of length m containing q_i and u_i)
syn.res<-sapply(syn.data,func,simplify="array")
print(syn.res)

#compute final estimates
regq.bar<-apply(syn.res[,1,],1,mean)
regu.bar<-apply(syn.res[,2,],1,mean)
regb.m<-apply(syn.res[,1,],1,var)

regT.p<-u.bar+regb.m/5

regq.bar
regu.bar
regb.m
regT.p


```



#5computation of confidence intervals
```{r}

#computation of the degrees of freedom
dfs<-(m-1)*(1+regu.bar/(regb.m/m))^2
dfs

#Confidence interval
l.95.syn<-regq.bar-qt(0.975,df=dfs)*sqrt(regT.p)
u.95.syn<-regq.bar+qt(0.975,df=dfs)*sqrt(regT.p)
ci.length.syn<-u.95.syn-l.95.syn
print(ci.length.syn)
print(l.95.syn)
print(u.95.syn)

#estimates from original data set cps
cps.res<-func(cps)
l.95.cps<-cps.res[,1]-1.96*sqrt(cps.res[,2])
u.95.cps<-cps.res[,1]+1.96*sqrt(cps.res[,2])
ci.length.cps<-u.95.cps-l.95.cps
print(ci.length.cps)
print(l.95.cps)
print(u.95.cps)

#comparison of the results
print(cbind(cps.res[,1],q.bar),digits=3)
print(cbind(ci.length.cps,ci.length.syn),digits=3)

#P-value for synthetic data
Tvalue <- (regq.bar-0) /regT.p^0.5
print(Tvalue)

pt(Tvalue,df=dfs)

Tvalue <- (regq.bar[15]-0) /regT.p[15]^0.5
Tvalue

pt(Tvalue,df=dfs[15])
pt


```

#6 plotting
```{r}
boxplot(income~sex,data=cps, main="", 
  	xlab="sex", ylab="income")

```

#special check from example: why are synthetic confidence intervals shorter for income?
qqplot(cps$income,syn.data[[1]]$income,
     ylim=c(min(cps$income,syn.data[[1]]$income),
      max(cps$income,syn.data[[1]]$income)))

qqplot(cps$income,syn.data[[1]]$income,
     ylim=c(min(cps$income,syn.data[[1]]$income),200000),
     xlim=c(min(cps$income,syn.data[[1]]$income),200000))
length(cps$income[cps$income>150000])
