---
title: "Lab Assignment footballdata"
author: "Elisabeth Linek"
output: html_document
---

## Lab Exercise: Explore Football Data

 This dataset containts soccer (or as Europeans prefer: football) player skill ratings
 (at the time of September 2011).
 The skill ratings are from the PES Stats Database (PSD), a community-based approach to
 create a database with accurate statistics and skill ratings for soccer players
 (originally for the video game "Pro Evolution Soccer" by Konami).

 It contains no less than 43 variables on 1851 players from 4 European Leagues
 (Bundesliga, La Liga, Premier League, Serie A).


## Tasks

 1. Visually explore the offensive (Attack) and defensive (Defence) skills of soccer players.

    But before going straight to the code, take a few minutes, think and take notes:
    a) What a priori expectations about the data and possible patterns do you have?
    b) What general exploration strategy would be appropriate?
    c) Which comparisons are possible and interesting?
    d) Which graphical formats would be useful to make these comparisons?

 2. Make sure you experiment with
    a) at least three graphical formats as well as
    b) with comparisons *within a single* plot and comparisons *across multiple* plots!

    If you are new to R, have a look at the following two videos
    on the course site:
    "surv752-code-05-Adding_Elements_to_an_Exisiting_Plot"
    "surv752-code-06-Arranging_Multiple_Plots"

 3. Finally, try to construct a "bullet graph" as invented by Stephen Few
    as well as a "slope graph" and "sparklines" as invented by Edward Tufte.
    (For these latter two graphical formats it's best to use data with a time
    component - so you may want to go back to the freedom house data.)
    For this exercise you my find the lines(), segments() and rect() plotting
    functions helpful.
 ___________________________________________


## 1. visual exploration

 helpful wrt. positions https://en.wikipedia.org/wiki/Association_football_positions

 a) What a priori expectations about the data and possible patterns do you have?
    * Forwards (offencive players) will have likely better offensive skills and defenders
      defensive players will have rather better defensive skills. Midfeilders will be likely
      in between depending on their position forward/defence the according skill will be
      higher (i.e. defensive midfielders (DMF) will have a higher defence skillset whereas
      offensive (AMF) will have a likely better offensive skillset).
    * Midfielders should have a higher passing accuracy than forwards.
    * Left footed players will play more likeley on the left side in case they don't play on
      both sides.
    * The four represented countries in the dataset represent the top four ranked countries
      in the UEFA association ranking by country of the season 2010-11. The order of the ranking
      was England, Spain, Italy and Germany at which England was ranked first (not the season
      ranking!).  This could be reflected in the dataset.
      https://en.wikipedia.org/wiki/2010%E2%80%9311_UEFA_Champions_League
      https://www.uefa.com/memberassociations/uefarankings/country/season=2010/index.html

 b) What general exploration strategy would be appropriate?
    * use the summary function
    * dplyr to group and and filter the data

 c) Which comparisons are possible and interesting?
    * Top n teams of the country vs the rest.
    * Player position distribution wrt. total number of players.
    * Avg. height by country
    * dribbling vs passing
    * Nationalities playing soccer in the four countries ->foreign vs. local
    * Attack/Defence wrt. age


 d) Which graphical formats would be useful to make these comparisons?
    * since it's just Attack and Defence to compare it's maybe best to go
      with small minimals to get a wider scope


```{r , warning = FALSE, message = FALSE}
options(tibble.print_max = Inf)
options(Encoding="UTF-8")

# tabelle - die die daten umreisst, überblick verschafft - wieviele spieler je liga?
# erste diagramme

library(dplyr)
library(grDevices)


football_data = read.csv("footballdata.csv")

summary(football_data)

football_data %>%
  group_by(Team) %>%
  summarise(meanA = mean(Attack), meanD = mean(Defence), n = n())

football_data %>%
  group_by(Nationality) %>%
  summarise(n = n())

overall_avg <- football_data %>%
  summarise(meanA = mean(Attack), meanD = mean(Defence), sdA = sd(Attack), sdD = sd(Defence))
overall_avg

pos_avg <- football_data %>%
  group_by(Position) %>%
  summarise(meanA = mean(Attack), meanD = mean(Defence), n = n()) %>%
  arrange(meanA, meanD)
pos_avg

```
## 2. experimental approximation

```{r , warning = FALSE, message = FALSE}
ad_by_age <- football_data %>%
  filter(!is.na(Age)) %>%
  group_by(Age, Position) %>%
  summarise(meanA = mean(Attack), meanD = mean(Defence), n = n()) %>%
  arrange(Age, meanA, meanD)

min_age <- ad_by_age$Age %>% min
max_age <- ad_by_age$Age %>% max

min_ma <- ad_by_age$meanA %>% min
max_ma <- ad_by_age$meanA %>% max

print('mean Attack and Defence by Age')
par(mfrow=c(2, 4))
for(i in pos_avg$Position){
  plot(ad_by_age$Age[ad_by_age$Position == i],
       ad_by_age$meanA[ad_by_age$Position == i],
       type='l',
       xlim=c(min_age, max_age),
       ylim=c(20,100),
       cex.main=1.5, cex.lab=1, cex.axis=.8,
       main=i,
       xlab='Age', ylab='mean Attack',
       panel.first=c(abline(h=pos_avg$meanA[pos_avg$Position == i], lty=2, col="grey")))
}
for(i in pos_avg$Position){
  plot(ad_by_age$Age[ad_by_age$Position == i],
       ad_by_age$meanD[ad_by_age$Position == i],
       type='l',
       xlim=c(min_age, max_age),
       ylim=c(20,100),
       cex.main=1.5, cex.lab=1, cex.axis=.8,
       main=i,
       xlab='Age', ylab='mean Defence',
       panel.first=c(abline(h=pos_avg$meanD[pos_avg$Position == i], lty=2, col="grey")))
}


colors <- c('red', 'yellow', 'blue', 'green')
leagues <- football_data$League %>% unique %>% sort
league_color_map <- setNames(as.list(colors), leagues)
league_color_map

par(mfrow=c(1, 1))
plot(NULL, xlim=c(0,100), ylim=c(0,100),
       xlab='Defence', ylab='Attack')
abline(h=overall_avg$meanA, lty=2, col="grey")
abline(v=overall_avg$meanD, lty=2, col="grey")
for (i in leagues) {
  points(football_data$Defence[football_data$League == i], football_data$Attack[football_data$League == i],
       pch=20,
       col=adjustcolor(league_color_map[[i]], alpha.f = 0.4))
}

# https://www.w3schools.com/charsets/ref_utf_symbols.asp
neuer <- c(football_data$Defence[football_data$Name == "Manuel Neuer"],
       football_data$Attack[football_data$Name == "Manuel Neuer"])
points(neuer[1], neuer[2], pch="⚽")
text(neuer[1], neuer[2], labels="Neuer", pos=3)

ronaldo <- c(football_data$Defence[football_data$Name == "Cristiano Ronaldo"],
       football_data$Attack[football_data$Name == "Cristiano Ronaldo"])
points(ronaldo[1], ronaldo[2], pch="⚽")
text(ronaldo[1], ronaldo[2], labels="Ronaldo", pos=3)

messi <- c(football_data$Defence[football_data$Name == "Leo Messi"],
       football_data$Attack[football_data$Name == "Leo Messi"])
points(messi[1], messi[2], pch="⚽")
text(messi[1], messi[2], labels="Messi", pos=3)



leagues <- c('Bundesliga', 'LaLiga', 'PremierLeague', 'SerieA')
nationality <- list('German', 'Spanish', list('English', 'Welsh'), 'Italian')
positions <- c("GK", "D", "M", "F")

national_player <- function(i) {
  return (football_data %>%
    filter(League == leagues[i], Nationality %in% nationality[[i]]) %>%
    group_by(Position) %>%
    summarise(meanA = mean(Attack), meanD = mean(Defence), n = n()) %>%
    arrange(meanA, meanD))
}

foreign_player <- function(i) {
  return (football_data %>%
    filter(League == leagues[i], !Nationality %in% nationality[[i]]) %>%
    group_by(Position) %>%
    summarise(meanA = mean(Attack), meanD = mean(Defence), n = n()) %>%
    arrange(meanA, meanD))
}

#inland
par(mfrow=c(2, 4))
for (i in 1:4)  {
  natp <- national_player(i)
  natp$Position <- factor(natp$Position, levels(natp$Position)[c(3, 1, 4, 2)])
  print(natp)
  forp <- foreign_player(i)
  forp$Position <- factor(forp$Position, levels(forp$Position)[c(3, 1, 4, 2)])
  plot(0, 0, xlim=c(1,4), ylim=c(20, 100), xaxt="n", main=leagues[i], xlab="Position", ylab="Attack")
  axis(1, at=1:4, labels=positions)
  points(natp$Position, natp$meanA, type="p", pch=20, col="red")
  points(forp$Position, forp$meanA, type="p", pch=20, col="blue")
}
for (i in 1:4)  {
  natp <- national_player(i)
  natp$Position <- factor(natp$Position, levels(natp$Position)[c(3, 1, 4, 2)])
  print(natp)
  forp <- foreign_player(i)
  forp$Position <- factor(forp$Position, levels(forp$Position)[c(3, 1, 4, 2)])
  plot(0, 0, xlim=c(1,4), ylim=c(20, 100), xaxt="n", main=leagues[i], xlab="Position", ylab="Defence")
  axis(1, at=1:4, labels=positions)
  points(natp$Position, natp$meanD, type="p", pch=20, col="red")
  points(forp$Position, forp$meanD, type="p", pch=20, col="blue")
}


```




```{r , warning = FALSE, message = FALSE}






```




## 3. bullet graph and slope graph

http://motioninsocial.com/tufte/
https://github.com/leeper/slopegraph


```{r , warning = FALSE, message = FALSE}


library("slopegraph")
data(gdp)
slopegraph(gdp, col.lines = 'gray', col.lab = "black",
           xlabels = c('1970', '1979'))

par(mfrow=c(2,1), mar=c(1,0,0,8), oma=c(4,1,4,4))
sparklines <- function(d, i) {
  plot(d[,i], lwd=0.5, axes=F, ylab="", xlab="", main="", type="l", new=F)
  axis(4, at=d[nrow(d),i], labels=d[nrow(d),i], tick=F, las=1, line=-1.5,
       family="serif", cex.axis=1.2)
  axis(4, at=d[nrow(d),i], labels=names(d[i]), tick=F, line=1.5,
       family="serif", cex.axis=1.4, las=1)
  text(which.max(d[,i]), max(d[,i]), labels=max(d[,i]),
       family="serif", cex=1.2, adj=c(0.5,3))
  text(which.min(d[,i]), min(d[,i]), labels=min(d[,i]),
       family="serif", cex=1.2, adj=c(0.5,-2.5))
  ymin <- min(d[,i])
  tmin <- which.min(d[,i])
  ymax<-max(d[,i])
  tmax<-which.max(d[,i])
  points(x=c(tmin,tmax), y=c(ymin,ymax), pch=19, col=c("red","blue"), cex=1)
  rect(0, summary(d[,i])[2], nrow(d), summary(d[,i])[4], border=0,
       col = rgb(190, 190, 190, alpha=90, maxColorValue=255))
}
sparklines(beaver1, 3)
sparklines(beaver2, 3)



library(ggplot2)

bullet.graph <- function(bg.data){

  # compute max and half for the ticks and labels
  max.bg <- max(bg.data$high)
  mid.bg <- max.bg / 2

  gg <- ggplot(bg.data)
  gg <- gg + geom_bar(aes(measure, high),  fill="goldenrod2", stat="identity", width=0.5, alpha=0.2)
  gg <- gg + geom_bar(aes(measure, mean),  fill="goldenrod3", stat="identity", width=0.5, alpha=0.2)
  gg <- gg + geom_bar(aes(measure, low),   fill="goldenrod4", stat="identity", width=0.5, alpha=0.2)
  gg <- gg + geom_bar(aes(measure, value), fill="black",  stat="identity", width=0.2)
  gg <- gg + geom_errorbar(aes(y=target, x=measure, ymin=target, ymax=target), color="red", width=0.45)
  gg <- gg + geom_point(aes(measure, target), colour="red", size=5)
  gg <- gg + scale_y_continuous(breaks=seq(0,max.bg,mid.bg))
  gg <- gg + coord_flip()
  gg <- gg + theme(axis.text.x=element_text(size=17),
                   axis.title.x=element_blank(),
                   axis.line.y=element_blank(),
                   axis.text.y=element_text(hjust=1, color="black"),
                   axis.ticks.y=element_blank(),
                   axis.title.y=element_blank(),
                   legend.position="none",
                   panel.background=element_blank(),
                   panel.border=element_blank(),
                   panel.grid.major=element_blank(),
                   panel.grid.minor=element_blank(),
                   plot.background=element_blank())

  return(gg)
}

fdf <- football_data %>%
  group_by(Team) %>%
  summarise(meanA = mean(Attack), meanD = mean(Defence), n = n())
fdf
mean(fdf$meanA)


df <- data.frame(
  measure=c("AC Chievo Verona"),
  high=c(100),
  mean=c(mean(football_data$Attack)),
  low=c(min(fdf$meanA)),
  target=c(max(fdf$meanA)),
  value=c(fdf$meanA[fdf$Team=="AC Chievo Verona"])
)

plot(bullet.graph(df))

df <- data.frame(
  measure=c("FC Bayern München"),
  high=c(100),
  mean=c(mean(football_data$Attack)),
  low=c(min(fdf$meanA)),
  target=c(max(fdf$meanA)),
  value=c(fdf$meanA[fdf$Team=="FC Bayern München"])
)

plot(bullet.graph(df))

df <- data.frame(
  measure=c("FC Barcelona"),
  high=c(100),
  mean=c(mean(football_data$Attack)),
  low=c(min(fdf$meanA)),
  target=c(max(fdf$meanA)),
  value=c(fdf$meanA[fdf$Team=="FC Barcelona"])
)

plot(bullet.graph(df))


```
